Fully Generalized Compilation

### 2017-02-02 papers/outline.tex

A \textbf{Full Generalized Compiler} is a tool for programming language researchers, providing a \textit{dynamic framework} for easily modifying syntax of input and output languages. The grammar of a programming language can be modified without recompiling the software. This is demonstrated by how easily a new programming language can be invented with Progtran. However, Progtran also uses this concept (dynamic syntax changes) to re-implement existing source-to-source compilation tools, such as \textbf{Cython} or \textbf{2to3}.

>>>>

A \textbf{Full Generalized Compiler} is a tool for programming language researchers, providing a \textit{dynamic framework} for easily modifying syntax of input and output languages. A new programming language can even be fully implemented without recompiling the software. However, Progtran also uses this concept (user defined dynamic grammars) to re-implement existing source-to-source compilation tools, such as \textbf{Cython} or \textbf{2to3}.
